---
title: "Dashboard Creation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dashboards}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rewardb)
```

## Creating a configuration file
First, you need to create a configuration YAML file. 
The best way to do this is to copy one of the existing configurations in the `config` directory.
E.g. open the file `../config/config.dev.yml` and save a copy `../config/config.my-study.yml`.

Now editing the new file you can set the application name, short_name and description fields.
The `short_name` field should be unique to your application because it is the postgres schema that the results will be stored in.
For this example we are only interested in two outcome ids and a custom atlas cohort.
Edit the fields in the top of the file as follows:

```
name: My study dashboard
short_name: my_study # This is the name of the database schema!
description: My study all about x
outcome_concept_ids: [] # These are atlas ids and  will not be multiplied by 100
custom_outcome_cohort_ids: [] # These are atlas ids and  will not be multiplied by 100
target_concept_ids: ~
```

Notice that the `target_cohort_ids` field has the character`~`, this indicates that the field is
null. This is because, for this example, we are interested in all exposures for the specified outcomes.

# Making the database 
Then we want to create the database schema and perform empirical calibration.

```{r eval = FALSE}
buildDashboardFromConfig("config/config.my-study.yml", "config/global-cfg.yml")
```
### Viewing the dashboard 
point at your new config file, e.g. `config/config.my-study.yml` relative to the current working directory.

Then to run the shiny application, inside R:
```{r eval = FALSE}
launchDashboard("config/config.tnfs.yml")
```